\cvsection{Publications}
\begin{cvhonors}
  \cventry
    {}
    {}
    {}
    {\textbf{Science}}
    {G. Valtolina, A. Burchianti, A. Amico, E. Neri, K. Xhani, J. A. Seman, A. Trombettoni, A. Smerzi, M. Zaccanti, M. Inguscio, G. Roati - “Josephson effect in fermionic superfluids across the BEC-BCS crossover” – Science  18 Dec 2015: Vol. 350, Issue 6267, pp. 1505-1508 DOI: 10.1126/science.aac9725}
  \cventry
    {}
    {}
    {}
    {\textbf{Nature Physics}}
    {G. Valtolina, F. Scazza, A. Amico, A. Burchianti, A. Recati, T. Enss, M. Inguscio, M. Zaccanti, and G. Roati. Exploring the ferromagnetic behaviour of a repulsive Fermi gas through spin dynamics. Nature Physics, 13(7):704–709, April 2017.}
  \cventry
    {}
    {}
    {}
    {\textbf{Physical Review Letters}}
    {F. Scazza, G. Valtolina, P. Massignan, A. Recati, A. Amico, A. Burchianti, C. Fort, M. Inguscio,  M. Zaccanti, and G. Roati. Repulsive Fermi Polarons in a Resonant Mixture of Ultracold Li 6 Atoms. Physical Review Letters, 118(8), February 2017.}
  \cventry
    {}
    {}
    {}
    {\textbf{Nuovo Cimento C}}
    {Andrea Amico. Experiments on the ferromagnetic behavior of atomic repulsive Fermi gases. Il Nuovo Cimento C, (2):1, August 2017.}
  \cventry
    {}
    {}
    {}
    {\textbf{Physical Review Letters}}
    {A. Burchianti, F. Scazza, A. Amico, G. Valtolina, J. A. Seman, C. Fort, M. Zaccanti, M. Inguscio, and G. Roati. Connecting Dissipation and Phase Slips in a Josephson Junction between Fermionic Superfluids.
Phys. Rev. Lett. 120, 025302 – Published 12 January 2018}
\end{cvhonors}















